\documentclass[12pt,oneside]{book}
\usepackage[letterpaper, left=1.2in, right=1.2in, top=1cm, bottom=1in]{geometry}
\pagestyle{plain}
\usepackage[pagestyles]{titlesec}
\usepackage{titletoc}
\usepackage{tocloft}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{float}
\usepackage{multirow}
\usepackage[toc,page]{appendix}
\usepackage{caption}
\setcounter{secnumdepth}{4}
\usepackage[backend=biber,style=apa,sorting=nyt]{biblatex} % apa citation style
\addbibresource{Reference.bib}
\usepackage[utf8]{inputenc}
\usepackage{appendix}
\usepackage{listings}
\usepackage{bm}
\titleformat{\chapter}%
  {\normalfont\bfseries\Huge}{\thechapter.}{10pt}{}
\newpagestyle{mystyle}{
  \sethead[][\thechapter.\enspace\chaptertitle][]{}{\thesection~\sectiontitle}{}
\setfoot{}{\thepage}{}}
\AtBeginDocument{\renewcommand{\bibname}{References}}

\captionsetup[figure]{margin=1.5cm,font=small,labelfont={bf},name={Figure},labelsep=colon,textfont={it}}
\captionsetup[table]{margin=1.5cm,font=small,labelfont={bf},name={Table},labelsep=colon,textfont={it}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Additional Material
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%========================================
% Title Page
%========================================
\input{Additional/TitlePage.tex}
\pagenumbering{roman}
\setcounter{page}{2}

%========================================
% Table of Contents
%========================================
\pagenumbering{roman} % Uncomment if Copyright and Acknowledgements are not in use
\setcounter{page}{2} % Uncomment if Copyright and Acknowledgements are not in use
\setcounter{tocdepth}{1}
\addcontentsline{toc}{chapter}{Table of Contents}
% \begin{doublespacing}
\tableofcontents
\clearpage
% \end{doublespacing}
% \currentpdfbookmark{Table of Contents}{TOC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Main Content
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% resume page numbering for rest of document
\pagenumbering{arabic}
\setcounter{page}{1} % set the page number appropriately

\input{Sections/1_Introduction.tex}
\input{Sections/2_Requirements.tex}
\input{Sections/3_Devices.tex}
\input{Sections/4_NetworkDesign.tex}
\input{Sections/5_Addressing.tex}
\input{Sections/6_Policies.tex}
\input{Sections/7_Security.tex}
\input{Sections/8_Monitoring.tex}
\input{Sections/9_DisasterPlan.tex}
\input{Sections/10_AdditionalProblems.tex}
\clearpage

% References
\begin{doublespace}
  \addcontentsline{toc}{chapter}{References}
  \printbibliography
\end{doublespace}

\begin{appendices}
\chapter{Cisco Hierarchical Model}
\label{appendix:layered-model}
This design uses the layered Core, Distribution, Access model approach to demonstrate the network structure. Each layer is represented by a different colour (Green = Access, Orange = Distribution, Blue = Core, and the Yellow = DMZ), and the tags on each section show the number of devices, name of the department, number of employees in each department and their floor numbers.
We are incorporating the Cisco three-layered hierarchical model to ensure scalability in line with Yotsuba Group's expansion. The model allows for ease of administration, network segregation and redundancy within the network to ensure a higher bandwidth availability. This is facilitated by the Layer three switches we have added to the distribution layer. These switches allow for routing between VLANs and enforcing security policies. The company will be able to review the components of their network and update where necessary. By having a clear hierarchical structure, the company will be able to monitor and effectively manage the network that has been designed.

\end{appendices}

\end{document}