\chapter{Monitoring and Maintenance}

Network Performance Monitoring and Maintenance
The network performance and maintenance strategy will focus on maintaining specific network performance goals. Ongoing evaluation of this strategy should be performed routinely, to ensure that it helps achieve the objectives outlined below:
\begin{itemize}
    \item Minimising network downtime
    \item Providing sufficient bandwidth
    \item Minimising latency
    \item Proactively identifying security or network issues
    \item Troubleshooting issues as quickly as possible
\end{itemize}

The tool of choice to help achieve this will be the Intermapper Network Monitoring Software, which provides mapping, monitoring and alerting solutions. It is an SNMPv3 enabled software, allowing for enhanced security and performance of monitoring network devices. Some key features include:
\begin{itemize}
    \item Automatic network mapping - colour-coded statuses on network devices provide the IT team with a visual indication of how the network is performing.
    \item Proactive network monitoring - SNMP protocol allows for continuous status updates for all devices, servers and applications.
    \item Remote network monitoring - geographically scattered devices and offices can be monitored, allowing for problems to be diagnosed and addressed remotely.
    \item Network traffic analysis - provides insight into bandwidth usage, traffic statistics and suspicious spikes or dips.
    \item Network automation - reduces manual network activities by executing pre-defined responses to alerts.
\end{itemize}

Other solutions on the market included software such as SolarWinds and Datadog and although they are more popular, two of the main factors in choosing Intermapper was due to its remote network monitoring and network automation features. As Yotsuba Group expands rapidly, there will be more instances of devices being spread across a larger geographical area. Intermapper bridges the gap so that those devices can still be monitored, but also issues on these devices can be resolved with a degree of automation.
The pricing of Intermapper also helps with the upscaling of Yotsuba Group in line with expansion, with prices varying depending on the number of devices that need to be monitored. Intermapper also comes with a risk-free 30-day trial so if for whatever reason it does not meet the requirements of the network, another provider can be sourced.